Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-07 paper/paper.tex
pass on text

Figure~\ref{fig:synflood-example} shows an
example rule of Suricata~\cite{suricata}, a popular open-source
\nids{}, maintained by the Open Information Security Foundation
(OISF)~\cite{oisf}. This example shows how Suricata can be used to
protect against SYN flood attacks. A TCP connection is typically
established with a 3-way handshake. First, the client sends a SYN
packet to the server, requesting a connection. Second, the server
responds with SYN-ACK packet to the client. Third, the client responds
with an ACK message and the connection is established. Aware of the
protocol, an attacker sends multiple SYN packets to different ports of
a server, often using fake IP addresses. Without proper protection,
the server accepts the connection requests and eventually legitimate
connection requests cannot be satisfied due to resource exhaustion.

>>>>

This section 1) presents an example of a network attack, 2) shows an
example rule of Suricata to detect this attack and alert system
administrators about it, and 3) illustrates how \tname{} performs to
synthesize the corresponding rule.

Let us recall that the 3-way handshake protocol in TCP/IP to establish
a TCP connection. First, a client sends a SYN packet to the server,
requesting a connection. Second, the server responds with SYN-ACK
packet to the client. Third, the client responds with an ACK message
and the connection is established.

Figure~\ref{fig:synflood-example} shows an
example rule of Suricata~\cite{suricata}, a popular open-source
\nids{}, maintained by the Open Information Security Foundation
(OISF)~\cite{oisf}. This example shows how Suricata can be used to
protect against SYN flood attacks.\Fix{explain the structure of the rule.}

Aware of the
protocol, an attacker sends multiple SYN packets to different ports of
a server, often using fake IP addresses. Without proper protection,
the server accepts the connection requests and eventually legitimate
connection requests cannot be satisfied due to resource exhaustion.
